---
title: "pop_up_graph"
format: html
editor: visual
---

## Quarto / Markdown Full screen graphs  / Pop Ups

Sometimes yopu have a big graph and you don't want to bombard your stakeholder with a massive graph but give them the otption to go more detailed if they want to.  

Or just have some content that is optional content on a popup

# Full Screen graph

Lets make a little graph and then make a button to make it big screen.

```{r}
#| echo: false
#| warning: false

library(tidyverse)
library(gt)

plot <- starwars |>
  filter(mass < 1000) |>
  ggplot(aes(x = height,
             y = mass,
             colour = gender)) +
  geom_point() +
  theme_minimal()

plot

```

<button type="button" class="btn btn-primary" data-bs-toggle="modal" data-bs-target="#examplePlot">See in Full Screen</button>

<div class="modal fade" id="examplePlot" tabindex="-1"><div class="modal-dialog modal-dialog-centered p-8" style="max-width: 90%"><div class="modal-content">

```{r}
#| echo: false
#| warning: false
#| out-width: "75%"
plot
```

</div></div></div>

# Independent popouts

Say we want the above but stick a table in it


<button type="button" class="btn btn-primary" data-bs-toggle="modal" data-bs-target="#exampleTable">Click for table</button>

<div class="modal fade" id="exampleTable" tabindex="-1"><div class="modal-dialog modal-dialog-centered p-8" style="max-width: 90%"><div class="modal-content">


```{r}
#| echo: false
#| warning: false
#| out-width: "75%"
starwars |> 
  slice_head(n=10) |>
  select (name,
          height,
          mass,
          hair_color,
          skin_color, 
          gender,
          homeworld
  ) |>
          gt()
```


</div></div></div>

All just additional touches of sparkle you can add to a markdown or quarto report.



